The Impact of Uncertainty on Monetary Transmission

### 2023-10-25 US/draft.Rmd
Comments revision round 1

---
title: "The Impact of Uncertainty on Monetary Transmission"
subtitle: "Evidence from the US"
author: "Péter Horváth" 
#date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  pdf_document:
    #toc: true
    #toc_depth: 3
    includes:
      in_header: "preamble.tex"
      before_body: "before_body.tex"
    number_sections: true
abstract: "This paper investigates the nonlinear interaction of the monetary transmission mechanism and economic uncertainty in the United States. I employ a Threshold VAR model with two states dependent on the level of uncertainty, and identify regime specific shocks using sign-restrictions. Results suggest that the short run contraction induced by the policy shock is large on the short term, however dissipates more quickly. Comparatively in low uncertainty times, the contraction is smaller with policymakers having a smoother control over the path the economy takes. The short-run larger impact can be leveraged to reduce inflation in a more cost-effective way, however the uncerlying cause of uncertainty needs to be carefully considered. "
fontsize: 12pt
bibliography: "ref.bib"
csl: "custom-citations.csl"
link-citations: true
linkcolor: "blue"
geometry: "a4paper,outer=25mm,inner=25mm,top=25mm,bottom=25mm"
---

@@

This paper serves as a natural followup to @horvathTBAuncertain. The paper establishes how the interest rate channel of the monetary transmission intertwined with economic uncertainty influences economies from across the globe. The results indicate that in times of high uncertainty, interest rate shocks lead to a larger contraction of macroeconomic demand, primarily reflecting in a larger and longer lasting slump in economic activity.

Works such as @aastveit2017economic and @aquino2022does, however, find opposing results, suggesting that uncertainty reduces transmission efficacy. The former use an interacted SVAR approach, where the regime indicator is interacted only with interest rates in the equations, and take the very far ends of the uncertainty distribution to define high and low uncertainty regimes. The latter criticizes this and argues for the use of a grid-search algorithm[^1] to find the optimal threshold level for the regime switches. Additionally their specification introduces the threshold assumption into the interest rate equation of the SVAR model - implying a state dependent Taylor Rule.

@@

This paper intends to fill this knowledge gap, by changing from a birds-eye view to a more microscopic perspective focusing on implications implications the United States. I adopt the same Threshold Vector-Autoregression (TVAR) model as well as sign-restriction approach to identify regime specific shocks. Following the previous paper, the core data behind the estimations are macroeconomic aggregates on a quarterly frequency, consisting of interest rates, inflation and GDP.

@@

Following such works, @caldara2016macroeconomic show that financial and uncertainty shocks are pivotal drivers of business cycles, exemplified during events like the Great Recession. Likewise, @bonciani2020international show that global financial uncertainty shocks bear down on economies, particularly in open economies during downturns.

@@

Such techniques are used for research on monetary policy as well. @avdjiev2014credit show that policy shocks have a more pronounced impact during low-growth periods while monetary policy having a aggressive responses during booms; @schmidt2020risk find evidence for state-dependency on asset prices, with macro-risk and policy risk playing distinct roles for the transmission; while @li2010financial and later @fry2016effects highlight monetary policy efficacy in times of financial stress, emphasizing short-term trade-offs between output and inflation.

@@

[^3]: The range of data does change in some specifications, as the Shadow Rate or the St. Louis Fed Financial Stress Index are only available on a shorter period of time.

@@

It is important to mention that there are a number of alternative[^5] measurements of uncertainty in the literature. These indices are for example the Equity Market-related Economic Uncertainty Index of @baker2016measuring; the Geopolitical Risk Index and the Trade Policy Uncertainty Index of @caldara2022measuring and @caldara2020economic; the World Uncertainty Index of @ahir2022world; as well as the VIX Index and the TED spread. In this paper, only the EPU and its Categorical indices are considered as measures of uncertainty.

@@

To address some potential issues, a number of robustness checks are conducted. Firstly, I replace the FFR in $Y_ {t}$ with the 1-Year Treasury Yield and the FFR shadow rate. Secondly, I check if the results hold if I change the construction of the regime indicator from $X_{t}$ to $X_{t-1}$, making it pre-determined, and thereby eliminating the potential of estimating the impact of two contemporaneous shocks. Thirdly, I incorporate the uncertainty index in its levels as well as a financial stress indicator in order to void their effects from the aggregates during the estimation.

@@

The identification of shocks is done using sign-restrictions, as with a relatively compact set of variables, this is the most straight-forward method. As standard macroeconomic theory dictates, I assume that an increase in interest rates should be a negative demand-type shock, and thus lead to a contraction of output and prices. In other terms, a positive sign-restriction is imposed on the interest rates, and a negative on inflation rates as well as GDP growth. Following @uhlig2005effects, the restriction is imposed on the contemporaneous effects, as well as up to 6 quarters ahead after the shock.

The algorithms proposed in @uhlig2005effects has some shortcomings that should be addressed. As pointed out by @arias2018inference, using the penalty algorithm has some adverse consequences. Firstly, this algorithm can introduce some unintentional sign restrictions on unrestricted variables, thereby leading to biased results. For the main round of estimations, this is no issue, as I work with a full set of sign restrictions. However more notably, the penalty algorithm accepts a larger number of posterior draws, thus narrowing confidence bands. Opposing to this, the rejection algorithm only accepts posterior draws where the impulse responses that exactly fit the imposed sign-restrictions. Additionally, @rubio2010structural proposed a more efficient rejection algorithm, and thus their improved algorithm is implemented in this paper.

In all cases, the models are estimated using Bayesian methods with a non-informative Wishart prior. The estimations yield a set of impulse response draws, which are aggregated into posterior-median impulse responses along with an 84% confidence interval. All computations are done in the R programming language relying on the work of @Danne2015 for the implementation of the sign-restriction algorithms.

@@

```{=latex}
\caption{Regime specific impulse responses, original specification. \label{fig:epumedirfs}}
\bigskip
\footnotesize
\textit{Notes}: The blue solid line represents the posterior median obtaied with the threshold value $\mu$ set to the median, the red one with it set to the 70th percentile of the EPU. The shaded areas represent the 84\% confidence bands calculated from the posterior impulse response draws.
\end{figure}
```
Results from this estimate suggest that the contemporaneous drop in output is slightly larger in low uncertainty, with the following quarters showing a similar level of contraction. Alongside this, a prolongued disinflation caused by the monetary shock can be observed in the high uncertainty regime. Comparing the two threshold levels, the changes in the impulse responses are close to negligible aside from the change in contemporaneous effects seen in the low regime.

These results are highly counter-intuitive, as they neither show reduced transmission efficacy, nor a prolonged contraction induced by the interest rate shock in high uncertainty times. The following subsections further investigate factors that might be key in shaping the regime specific responses.

@@

The results of these tests suggests that in most cases we fail to reject the null, and thus policy shocks do not drive uncertainty, neither the other way around. Interpreting the p-values as the likelihood of $H_{0}$ to be true, there are a handful of conclusions to draw. The likelihood of policy shocks driving uncertainty stay reasonably high irrespective of specification, however, for the reverse causality case, it varies substantially. Firstly, the likelihood of uncertainty being a driver of policy shocks considerably increases when switching from the median to the 70th percentile threshold. This is likely due to the low number of observations in the regime, and thus an increased likelihood of policy action being taken to mitigate the negative impact of uncertainty. Secondly, using the Shadow rate[^7] over the FFR also considerably reduces this likelihood. Given these, the superior specification should be a TVAR with a full set of controls estimated with the threshold level set to the median. The next subsection showcases the impulse responses estimated from this.

@@

```{=latex}
\caption{Regime specific impulse responses, extended model. \label{fig:updatedirfs}}
\bigskip
\footnotesize
\textit{Notes}: In the extended model, interest rates are measured by the FFR, the threshold value is set to the median of the EPU index, lagged values of the EPU and the St. Louis FED Financial Stress Indicator are added as controls.
\end{figure}
```
Results from the extended model imply that to some extent findings from the previously cited literature on this question all have some truths to them. In high uncertainty times, the impact of the monetary shock is considerably elevated on impact, and the first few quarters after the shock. However, dissipates much more rapidly from the variables, even reverting from disinflation to inflation around 12-16 quarters after the shock. The larger impact around the time of the shock supports the idea, that uncertainty inflates the variance of expectations, and thereby increasing the impact of shocks.

On the other hand, in times of low uncertainty, the impact is comparatively smaller, however the persistence of the impulse responses is greater, leading to the the adjustment of prices and output being slower, staying below 0 over the 20 quarter horizon. This indicates lower variance and more stability in the expectations of agents in the economy.

@@

In @baker2016measuring, additional to the EPU index, several categorical indices are constructed[^9]. To investigate how the underlying cause behind uncertainty interacts with the transmission mechanism, I replicate the estimation with each of these categorical indices. To compare how much the narrative of uncertainty matters, I calculate sacrifice ratios - foregone output as a fraction of deterred inflation - from accumulated impulse responses over 4, 12 and 20 quarters for both high and low uncertainty regimes. To further aggregate, I calculate the sacrifice ratio of the high uncertainty regime relative to the low uncertainty regime. These can be seen below in Figure \ref{fig:narrative}.

@@

```{=latex}
\begin{figure}[!htbp]
```
```{r narrative, fig.width=10}
irfs %>% 
  select(-mult, -restr) %>% 
  filter(label != 'R',
         spec == 'main',
         #index != 'epu',
         control == 'both',
         thresh == '0.5') %>% 
  group_by(label, regime, spec, control, thresh, index) %>% 
  mutate(median = purrr::accumulate(.x = median, 
                                    .f = sum,
                                    .dir = 'forward'),
         upper = purrr::accumulate(.x = upper, 
                                   .f = sum,
                                   .dir = 'forward'),
         lower = purrr::accumulate(.x = lower, 
                                   .f = sum,
                                   .dir = 'forward')) %>% 
  filter(t  %in% c(4, 12, 20)) %>%
  mutate(t = case_when(t == 4 ~ '1-year',
                       t == 12 ~ '3-year',
                       t == 20 ~ '5-year')) %>% 
  select(-upper, -lower) %>% 
  spread(label, median) %>% 
  mutate(sac = Y/PI,
         regime = str_remove_all(regime, ' uncertainty'),
         index = case_when(index == 'epu' ~ 'EPU',
                           index == 'epu_debt' ~ 'EPU: Debt, crises',
                           index == 'epu_finreg' ~ 'EPU: Fin. Regulation',
                           index == 'epu_fis' ~ 'EPU: Fiscal Policy',
                           index == 'epu_mon' ~ 'EPU: Monetary Policy',
                           index == 'epu_reg' ~ 'EPU: Regulation',
                           index == 'epu_trade' ~ 'EPU: Trade Policy')) %>% 
  select(-PI, -Y) %>% 
  spread(regime, sac) %>% 
  mutate(relsac = High/Low) %>% 
  ggplot(aes(x = t, y = relsac, fill = t)) +
  geom_col(color = 'black') +
  facet_wrap(~index, nrow = 1) +
  theme_minimal()+
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  labs(x = '',
       y = '') +
  scale_fill_brewer('Set 1', direction = -1)
```

```{=latex}
\caption{Sacrifice ratios. \label{fig:narrative}}
\bigskip
\footnotesize
\textit{Notes}: The ratios are calculated from impulse responses obtained using the extended model.  
\end{figure}
```
For most measures, the relative sacrifice ratio decreases over time, which is no surprise given the results seen in Figure \ref{fig:updatedirfs}. However, many of these relative sacrifice ratios show values below one, meaning the trade-off between reducing inflation and forgoing growth is smaller in high uncertainty. Calculated over the longer run, this is not necessarily counterintuitive, as responses in the low uncertainty regime stay more persistently below zero, however on the shorter run (1-year) this implies that policy authorities can leverage the higher variance the impact on prices is reflected disproportionately higher on prices than output - however taking into account the underlying cause matters significantly.

An exception in Figure \ref{fig:narrative} being uncertainty related to sovereign debt and currency crises. Here the high uncertainty sacrifice ratio is larger on the short run and increases over longer horizons. High uncertainty around debt can increase borrowing costs for the government - potentially necessitating austerity measures. An increased demand from governments for debt financing would likely crowd out private investments. A rate hike in such context would add further pressure on government debt schedules and thus enlarge the crowding out effect by either the issuance of new debt or tax increases, carrying over to future periods.

@@

As noted in the the Methodology section, there could be two arguments against the specification used to obtain the results seen above. One of them being using time $t$ values of the EPU to specify the regimes, the other being that the variables should be voided of the share of variance explained by uncertainty. The former is achievable by changing Equation \ref{eq:1} to use $X_{t-1}$ instead of $X_{t}$ for specifying the regime indicator, while the latter is done as shown in \ref{eq:2}. Figure \ref{fig:contemp} shows that the outcomes obtained from such alternative specifications is largely similar. Two notable differences are i) when uncertainty is controlled for and the $t-1$ value of the index is used for constructing the indicator, the high uncertainty inflation response is slightly dampened; and ii) both inflation and output responses sharpen in high uncertainty when switching from a $t$ to a $t-1$ quarter-based indicator. These however do not cause robustness concerns and indicate that the four-quarter lag of each variable are sufficient controls, as the former of the two differences is relatively minor, while the latter is washed out of the results once the level of uncertainty is also controlled for - yielding results alike to the baseline specification of Equation \ref{eq:1}.

@@

Voiding the effects of financial stress is also a crucial determinant in shaping the results. As seen in Figure \ref{fig:finstress}, after including the financial stress indicator as a control variable, the responses shift downwards drastically, especially in the lower regime. Switching the threshold variable from the median to the 70th percentile, the low uncertainty responses turn almost unaffected, however high regime responses show a drastically increased drop.

>>>>

---
title: "The Impact of Uncertainty on Monetary Transmission"
subtitle: "Evidence from the US"
author: "Péter Horváth" 
#date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  pdf_document:
    #toc: true
    #toc_depth: 3
    includes:
      in_header: "preamble.tex"
      before_body: "before_body.tex"
    number_sections: true
abstract: "This paper investigates the nonlinear interaction of the monetary transmission mechanism and economic uncertainty in the United States. I employ a Threshold VAR model with two states dependent on the level of uncertainty, and identify regime specific shocks using sign-restrictions. Results suggest that the short run contraction induced by the policy shock is larger when uncertainty is high, however, in such times, its impact dissipates more quickly. Comparatively in low uncertainty times, the contraction is smaller with policymakers having a smoother control over the path the economy takes. The short-run larger impact can be leveraged to reduce inflation in a more cost-effective way, however the uncerlying cause of uncertainty needs to be carefully considered. "
fontsize: 12pt
bibliography: "ref.bib"
csl: "custom-citations.csl"
link-citations: true
linkcolor: "blue"
geometry: "a4paper,outer=25mm,inner=25mm,top=25mm,bottom=25mm"
---

@@

The transmission of monetary policy interventions has been a cornerstone of macroeconomic research for academics and policymakers alike, as understanding how monetary policy can affect the real economy has consequential implications for evaluating the right policy strategy. Another field gaining increased attention, especially for empirical macroeconomists, is research on how uncertainty drives business cycles. The literature agrees that uncertainty is an important driver of macroeconomic demand, primarily influencing it through investment decisions. However, the interplay between uncertainty and the monetary transmission mechanism is relatively less investigated. This leads to the purpose of this paper: To extend the existing literature in quantifying how uncertainty - especially uncertainty related to economic policy - affects the transmission mechanism.

Primarily, this paper is a natural followup to @horvathTBAuncertain. The paper establishes how the interest rate channel of monetary transmission in times of elevated global economic uncertainty arising from geoeconomic fragmentation influences economies. The results indicate that in times of high uncertainty, interest rate shocks lead to a larger contraction of macroeconomic demand, primarily reflecting in a larger and longer lasting slump in economic activity.

Earlier works in this field, such as @aastveit2017economic and @aquino2022does, however, find opposing results, suggesting that uncertainty reduces transmission efficacy. The former use an interacted SVAR approach, where the regime indicator is interacted only with interest rates in the equations, and take the very far ends of the uncertainty distribution to define high and low uncertainty regimes. The latter criticizes this and argues for the use of a grid-search algorithm[^1] to find the optimal threshold level for the regime switches. Additionally their specification introduces the threshold assumption into the interest rate equation of the SVAR model - implying a state dependent Taylor Rule.

@@

This paper intends to fill this knowledge gap, by changing from a birds-eye view to a more microscopic perspective focusing on implications for the United States. I adopt the same Threshold Vector-Autoregression (TVAR) model as well as sign-restriction approach to identify regime specific shocks. To measure the transmission of monetary shocks, I employ a set of quarterly macroeconomic as my core dataset comprising of interest rates, inflation and GDP, and as such, it is possible to measure the transmission of policy shocks to the real economy.

@@

@caldara2016macroeconomic show that financial and uncertainty shocks are pivotal drivers of business cycles, exemplified during events like the Great Recession. Likewise, @bonciani2020international show that global financial uncertainty shocks bear down on economies, particularly in open economies during downturns.

@@

Such techniques are used for research on monetary policy as well. @avdjiev2014credit show that policy shocks have a larger impact in recession periods, and that monetary policy reacts more aggressively to rising inflation during booms; @schmidt2020risk find evidence for state-dependency on asset prices, with macro-risk and policy risk playing distinct roles for the transmission; while @li2010financial and later @fry2016effects highlight monetary policy efficacy in times of financial stress, emphasizing short-term trade-offs between output and inflation.

@@

[^3]: Data for interest rates, inflation and economic activity is available from much earlier, however the sample is restricted to start from `r max(min(data2[['uncertainty']][['date']]), min(data2[['macro']][['date']])) %>% quarterly_format()` as it is the earliest available data point for the EPU index. The range of data does change in some specifications, as the Shadow Rate or the St. Louis Fed Financial Stress Index are only available on a shorter period of time.

@@

It is important to mention that there are a number of additional[^5] measurements of uncertainty in the literature. Measures such as the VIX Index and the TED spread using market data, as well as the search-term based Equity Market-related Economic Uncertainty Index of @baker2016measuring can be used to grasp uncertainty in financial and liquidity markets. @caldara2022measuring and @caldara2020economic use textual data to construct the Geopolitical Risk Index and the Trade Policy Uncertainty index which measure uncertainty around geopolitical and trade tensions. @ahir2022world use text searches in Country Intelligence Unit reports to construct the World Uncertainty Index, as a broader measure of uncertainty. As this paper focuses on the implications of uncertainty for monetary policy, I use only the EPU and its Categorical indices as they are the most tailored to grasping uncertainty around economic policy.

@@

To address some potential issues, a number of robustness checks are conducted. Firstly, I replace the FFR in $Y_ {t}$ with the 1-Year Treasury Yield and the FFR shadow rate. Secondly, I check if the results hold if I change the construction of the regime indicator from $X_{t}$ to $X_{t-1}$, making it pre-determined, and thereby eliminating the potential of estimating the impact of two contemporaneous shocks. Thirdly, I incorporate the uncertainty index in its levels as well as a financial stress indicator in order to purge their effects from the aggregates during the estimation.

@@

Empirically, an obstacle in estimating impulse responses that show the correct sign associated with monetary shocks is the price puzzle. Estimating a trivariate (interest rates - inflation - GDP) SVAR model yields impulse responses showing a rise in inflation as a consequence of an interest rate shock. This, however goes against standard macroeconomic theory, which states that increasing policy rates should contract macroeconomic demand and thus lead to a decline both in prices as well as output. Numerous authors (among others @hanson2004price, @giordani2004alternative, @demiralp2014still, @bishop2017anticipatory, @cloyne2016macroeconomic, @romer2004new) investigate the price puzzle, suggesting different explanations or ways of dealing with this phenomenon.

In this paper, I follow a different branch of literature. Pioneered by @uhlig2005effects, it is possible to incorporate some prior beliefs into the estimation by imposing sign-restrictions on the impulse responses. His seminal work introduces a (full-Bayesian) rejection as well as a penalty algorithm for estimating SVAR-s as such. The former approach accepts impulse response draws only if they exactly fit the imposed restrictions. The latter accepts draws that violate the sign-restrictions using a goodness-of-fit based penalty score.

At first glance, the penalty approach might seem more desirable due to higher flexibility, however @arias2018inference show some adverse properties of this algorithm. Firstly, the penalty algorithm can artificially impose restrictions on the unrestricted variable, and secondly, the - by design - higher number of accepted responses narrows confidence bands. In a smaller model, such as the trivariate one with a full set of restrictions is no issue, however, if the model is extended with variables on which no restrictions are placed this would be an issue, and the narrower confidence bands would misrepresent the accuracy of the results. Additionally, @rubio2010structural improved on the efficiency of the rejection algorithm of @uhlig2005effects, and for these reasons, their iteration of it is used in this paper.

In all estimations, Bayesian models are estimated with 4 lags and a non-informative Wishart prior. For the purposes of this paper, partial identification is sufficient, and as such, sign-restrictions are only imposed on monetary shocks.The sign-restriction is imposed to follow common macroeconomic assumptions, meaning a positive sign on interest rates and negative on inflation and output. The mirror image of the results can be obtained by reversing the sign restrictions, and I assume the impulse responses are independent of the size of the monetary shock. As such, studying sign and size asymmetries is left for future research.

Posterior impulse responses are estimated in a bootstrap simulation with 200 impulse response draws for each 20000 MCMC replication. These are computed separately for both the low and the high uncertainty regime in each case. The accepted posterior impulse responses are aggregated into posterior-medians along with and 84% confidence interval. All computations are done in the R programming language relying on the work of @Danne2015 for the implementation of the sign-restriction algorithms.

@@

```{=latex}
\caption{Regime specific impulse responses, original specification. \label{fig:epumedirfs}}
\bigskip
\footnotesize
\textit{Notes}: The blue solid line represents the posterior median obtaied with the threshold value $\mu$ set to the median, the red one with it set to the 70th percentile of the EPU. The shaded areas represent the 84\% confidence bands calculated from the posterior impulse response draws.
\end{figure}
```

Results from this estimate suggest that the contemporaneous drop in output is slightly larger in low uncertainty, with the following quarters showing a similar level of contraction. Alongside this, a prolongued disinflation caused by the monetary shock can be observed in the high uncertainty regime. Comparing the two threshold levels, the changes in the impulse responses are close to negligible aside from the change in contemporaneous effects seen in the low regime. Such results are not supported by either of the previous literature. In the following subsections I investigate if other factors could be influential in shaping the impulse responses.

@@

The results of these tests suggests that in most cases we fail to reject the null, and thus policy shocks do not drive uncertainty, neither the other way around. Interpreting the p-values as the likelihood of $H_{0}$ to be true, there are a handful of conclusions to draw. The likelihood of policy shocks driving uncertainty stay reasonably low irrespective of specification, however, for the reverse causality case, it varies substantially. Firstly, the likelihood of uncertainty being a driver of policy shocks considerably increases when switching from the median to the 70th percentile threshold. This is likely due to the low number of observations in the regime, and thus an increased likelihood of policy action being taken to mitigate the negative impact of uncertainty. Secondly, using the Shadow rate[^7] over the FFR also considerably reduces this likelihood. Given these, the superior specification should be a TVAR with a full set of controls estimated with the threshold level set to the median. The next subsection showcases the impulse responses estimated from this.

@@

```{=latex}
\caption{Regime specific impulse responses, extended model. \label{fig:updatedirfs}}
\bigskip
\footnotesize
\textit{Notes}: In the extended model, interest rates are measured by the FFR, the threshold value is set to the median of the EPU index, lagged values of the EPU and the St. Louis FED Financial Stress Indicator are added as controls.
\end{figure}
```

Partially, the results of the extended model are supported from findings of the previous literature. In low uncertainty times, we see that the policy shock has a comparatively smaller advantage, however, the adjustment is slower, steadier and more persistent over the 20 quarter horizon, likely meaning that the central bank has a better control over future expectations. However, in high uncertainty times, the initial contraction in the first few quarters is larger, and dissipates more quickly. Additionally, the estimated impulse responses are much less smooth, and around 12 quarters after the intervention, a rise in inflation can be observed. These could be signs that high uncertainty times cause the variance of future expectations to be larger, in turn causing shocks to have larger impacts on one hand, while on the other causing the less persistent responses.

@@

In @baker2016measuring, additional to the EPU index, several categorical indices are constructed[^9]. To investigate how the underlying cause behind uncertainty interacts with the transmission mechanism, I replicate the estimation with each of these Categorical indices. For this estimation I use the extended model with the threshold set to the median - as seen in the previous subsection - of each Categorical EPU index.

To compare across estimates, I calculate sacrifice ratios as $Sacrifice Ratio = \frac{\Delta Output}{\Delta Inflation}$ for both uncertainty regimes. In essence, these capture how much output (growth) was forgone at the cost of deterring a percentage point of inflation. These ratios are calculated over a 1-year (4-quarter), 3-year (12-quarter) and 5-year (20-quarter) horizon.

I perform a further round of aggregation, and calculate the relative sacrifice ratio of high uncertainty sacrifice ratios as a fraction of low uncertainty ones. These can be interpreted as how much more (less) the cost is of deterring inflation when uncertainty is high compared to low uncertainty times. The relative sacrifice ratios can be seen below in Figure \ref{fig:narrative}.

@@

```{=latex}
\begin{figure}[!htbp]
```
```{r narrative, fig.width=10}
irfs %>% 
  select(-mult, -restr) %>% 
  filter(label != 'R',
         spec == 'main',
         #index != 'epu',
         control == 'both',
         thresh == '0.5') %>% 
  group_by(label, regime, spec, control, thresh, index) %>% 
  mutate(median = purrr::accumulate(.x = median, 
                                    .f = sum,
                                    .dir = 'forward'),
         upper = purrr::accumulate(.x = upper, 
                                   .f = sum,
                                   .dir = 'forward'),
         lower = purrr::accumulate(.x = lower, 
                                   .f = sum,
                                   .dir = 'forward')) %>% 
  filter(t  %in% c(4, 12, 20)) %>%
  mutate(t = case_when(t == 4 ~ '1-year',
                       t == 12 ~ '3-year',
                       t == 20 ~ '5-year')) %>% 
  select(-upper, -lower) %>% 
  spread(label, median) %>% 
  mutate(sac = Y/PI,
         regime = str_remove_all(regime, ' uncertainty'),
         index = case_when(index == 'epu' ~ 'EPU',
                           index == 'epu_debt' ~ 'EPU: Debt, crises',
                           index == 'epu_finreg' ~ 'EPU: Fin. Regulation',
                           index == 'epu_fis' ~ 'EPU: Fiscal Policy',
                           index == 'epu_mon' ~ 'EPU: Monetary Policy',
                           index == 'epu_reg' ~ 'EPU: Regulation',
                           index == 'epu_trade' ~ 'EPU: Trade Policy')) %>% 
  select(-PI, -Y) %>% 
  spread(regime, sac) %>% 
  mutate(relsac = High/Low) %>% 
  ggplot(aes(x = t, y = relsac, fill = t)) +
  geom_col(color = 'black') +
  facet_wrap(~index, nrow = 1) +
  theme_minimal()+
  theme(legend.position = 'none') +
  theme(axis.text.x = element_text(angle = 45, vjust = 0.5, hjust=1)) +
  labs(x = '',
       y = '') +
  scale_fill_brewer('Set 1', direction = -1)
```
```{=latex}
\caption{Sacrifice ratios. \label{fig:narrative}}
\bigskip
\footnotesize
\textit{Notes}: The ratios are calculated from impulse responses obtained using the extended model.  
\end{figure}
```

For most of these, we can observe that the relative sacrifice ratio is decreasing over time. This is no surprise, given the results seen in Figure \ref{fig:updatedirfs}, seeing as the impact of the policy shock contracts output and prices more persistently in the low regime, and dissipates quicker in the high regime. Additionally, we can observe that for a number of the Categorical EPU indices, the relative sacrifice ratio starts and stays below one, meaning that deterring inflation comes at a lower cost. However, Figure \ref{fig:narrative} also warns us that the underlying cause behind uncertainty needs to be carefully considered.

For example, uncertainty related to sovereign debt and currency crises tells a much different story compared to what can be seen from the other indices. Here the high uncertainty sacrifice ratio is larger on the short run and increases over longer horizons. High uncertainty around debt can increase borrowing costs for the government - potentially necessitating austerity measures. An increased demand from governments for debt financing would likely crowd out private investments. A rate hike in such context would add further pressure on government debt schedules and thus enlarge the crowding out effect by either the issuance of new debt or tax increases, carrying over to future periods.

@@

As noted in the the Methodology section, there could be two arguments against the specification used to obtain the results seen above. One of them being using time $t$ values of the EPU to specify the regimes, the other being that the variables should be purged of the share of variance explained by uncertainty. The former is achievable by changing Equation \ref{eq:1} to use $X_{t-1}$ instead of $X_{t}$ for specifying the regime indicator, while the latter is done as shown in \ref{eq:2}. Figure \ref{fig:contemp} shows that the outcomes obtained from such alternative specifications is largely similar. Two notable differences are i) when uncertainty is controlled for and the $t-1$ value of the index is used for constructing the indicator, the high uncertainty inflation response is slightly dampened; and ii) both inflation and output responses sharpen in high uncertainty when switching from a $t$ to a $t-1$ quarter-based indicator. These however do not cause robustness concerns and indicate that the four-quarter lag of each variable are sufficient controls, as the former of the two differences is relatively minor, while the latter is washed out of the results once the level of uncertainty is also controlled for - yielding results alike to the baseline specification of Equation \ref{eq:1}.

@@

Purging the effects of financial stress is also a crucial determinant in shaping the results. As seen in Figure \ref{fig:finstress}, after including the financial stress indicator as a control variable, the responses shift downwards drastically, especially in the lower regime. Switching the threshold variable from the median to the 70th percentile, the low uncertainty responses turn almost unaffected, however high regime responses show a drastically increased drop.
